Irt plot extra

### 2022-03-24 manuscript.Rmd
EFA plots are now 2 by 2

#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

install.packages("correlation")
#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
library(koRpus)# stable release
library(koRpus.lang.en)
library(reshape)
library(ggsci)
r_refs("references.bib")
```

@@

```{r Manuflowchart, include=FALSE }
#This chunk holds code for the work flow chart of the data analysis

@@

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)

@@

ggsave("Manuscript.figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 600 )
```

@@

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

full.tab.1 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 01-24 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
 gtsave("Manuscript.figures/gt_full_p1.png", vwidth = 6000)

full.tab.2 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 24-48 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("LEBA  Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
gtsave("Manuscript.figures/gt_full_p2.png",vwidth = 6000)

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Manuscript.figures/gt_full_p1.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Manuscript.figures/gt_full_p2.png')

@@

  gtsave("Supplimentary_Materials/S_Figure/S1_Fig.png", vwidth=6000)

@@

ggsave("Manuscript.figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
```

@@

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")

(ref:figCor) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than |.30|

```{r figCor, out.height="150%",out.width="100%", fig.align= 'center', fig.cap='(ref:figCor)', results='asis', fig.align='center'}

knitr::include_graphics('Manuscript.figures/corplot.png', dpi =600)

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
  apatheme +theme(legend.position = "None") +scale_fill_identity()

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

```{r factors, include=F}
#This chunk holds code for compiled factor identification plots

fator <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
```

```{r factorsplot, eval=FALSE, include=FALSE}
#This chunk holds code for compiled factor identification plots

fator2 <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=3, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors2.png",fator2, width = 18, height = 6, dpi = 600)
```

(ref:facIdFig) Factor Identification Methods  (A) Scree plot suggested six factors. (B) Hull method indicated 5 factors were required to balance the model fit and number of parameters.

```{r facIdFig, fig.align= 'center', fig.cap='(ref:facIdFig)',  warning=FALSE, results= 'asis'}

knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)

@@

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png",dpi =600)

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:efagtPic) depicts the data distribution and endorsement pattern for the included 25 items. Figure \@ref(fig:EFAplot)(A) depicts the five factor structure obtained in EFA. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

@@

```{r EFAplotprep, include=F}
#This chunk holds codes for co-plotting EFA-plot and residual plot.

@@

img1 <- png::readPNG("Manuscript.figures/EFAplot.png")

@@

ggsave("Manuscript.figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")

@@

```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, include=FALSE, results='asis'}

knitr::include_graphics('Manuscript.figures/gt_full.png', dpi =600)
```

```{r ft-CFA, include =F}
gt.cfa.data <- gt.data[429:690,]
gt.cfa.data.table <- gt.cfa.data %>% 
  dplyr::select(item16, item36, item17,
                 item11, item10,item12,item07,item08,item09,
                 item27,  item03, item40,  item30, item41,
                 item32,item35,item38, item33, 
                 item46, item45, item25, item04, item01 )

@@

cfa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**Light Exposure Behavior Assessment**"),
    subtitle = md("Summary Descriptives CFA Sample (n=262)")
  ) %>% 
  # tab_footnote(
  #   footnote = md("**Histogram**"),
  #   locations = cells_column_labels(columns = hist_data)
  # ) %>%
  # tab_footnote(
  #   footnote = md("**Density**"),
  #   locations = cells_column_labels(columns = dens_data)
  # ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = (""),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5: Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F4: Using light before bedtime**"),
      rows = c(15,16,17,19) 
        ) %>% 
  tab_row_group(
      label = md("**F3: Using phone and smart-watch in bed**"),
      rows = c(2,13,14,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F2: Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1: Wearing blue light filters**"),
      rows = c(10,11,18) 
        ) %>% 
  gtsave("Supplimentary Materials/S_Figure/cfagt.png",vwidth = 7000)

@@

png(filename="Manuscript.figures/CFAplot2.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

knitr::include_graphics("Manuscript.figures/CFAplot.png", dpi =600)

@@

ggsave("Manuscript.figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")

@@

ggsave("Manuscript.figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")

@@

TIC.plot <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 3,
                     label_size = 15,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")

@@

knitr::include_graphics('Manuscript.figures/TIC.png', dpi =600)
```

>>>>

#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot,ggtext)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

install.packages("correlation")
install.packages("ggtext")
#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
library(koRpus)# stable release
library(koRpus.lang.en)
library(reshape)
library(ggsci)
library(ggtext)
r_refs("references.bib")
```

@@

```{r Manuflowchart, eval=FALSE, include=FALSE}
#This chunk holds code for the work flow chart of the data analysis

@@

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Figures/Flowchart1.jpeg", dpi = 600)

@@

ggsave("Figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
knitr::include_graphics('Figures/Flowchart.png', dpi = 600 )
```

@@

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
knitr::include_graphics('Figures/distribution.png', dpi = 300 )
```

@@

full.tab.1 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 01-24 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
 gtsave("Figures/gt_full_p1.png", vwidth = 6000)

full.tab.2 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 24-48 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("LEBA  Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
gtsave("Figures/gt_full_p2.png",vwidth = 6000)

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Figures/gt_full_p1.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Figures/gt_full_p2.png')

@@

  gtsave("Supplimentary_materials/S_Figure/S1_Fig.png", vwidth=6000)

@@

# ggsave("Figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
```

@@

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.2,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 6),
         axis.text.y = element_text(size = 6),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#to show pvalue in the fig add p.mat=p.mat
# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
  scale_x_continuous(name="Factor Number", limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
  apatheme +theme(legend.position = "None") +scale_fill_identity()

@@

Scree plot ( Figure \@ref(fig:efa-plot)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Figures/EFAplot.png",dpi =600)

@@

```{r efa-plot, include=F}
#This chunk holds code for compiled factor identification plots

cor.scree <- cowplot::plot_grid(corplot, scree.plot,
                                labels = c("A", "B"),
                                nrow =1, ncol =2,
                                rel_widths = c(2, 1),
                                label_fontfamily = "Arial",
                  label_fontface = "plain")

hull.residual <- cowplot::plot_grid(Hull, residual.plot,
                                labels = c("C", "D"),
                                nrow =1, ncol =2,
                                                                label_fontfamily = "Arial",
                  label_fontface = "plain")

efa.plot <- cowplot::plot_grid(cor.scree, hull.residual,

                                nrow =2)

# efa.plot <- cowplot::plot_grid(corplot , scree.plot,Hull, residual.plot,
#                    labels = "AUTO",
#                    ncol=2,nrow=2, 
#                   align = "v", 
#                   label_fontfamily = "Arial",
#                   label_fontface = "plain")
ggsave("Figures/efa.plot.png",efa.plot, width = 7, height = 8, dpi = 600)
```

(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than |.30|. (B) Scree plot suggested six factors. (C) Hull method indicated 5 factors were required to balance the model fit and number of parameters. (D) Histogram of nonredundent residual correlations indicated 26% of inter-item correlations were higher than .05, hinting a possible under factoring.

```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis'}

knitr::include_graphics('Figures/efa.plot.png', dpi =600)

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

@@

```{r EFAplotprep, eval=FALSE, include=FALSE}
#This chunk holds codes for co-plotting EFA-plot and residual plot.

@@

img1 <- png::readPNG("Figures/EFAplot.png")

@@

ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")

@@

```{r gt-CFA, include =F}
gt.cfa.data <- gt.data[429:690,]
gt.cfa.data.table <- gt.cfa.data %>% 
  dplyr::select(item16, item36, item17,
                 item11, item10,item12,item07,item08,item09,
                 item27,  item03, item40,  item30, item41,
                 item32,item35,item38, item33, 
                 item46, item45, item25, item04, item01 )

@@

cfa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**Light Exposure Behavior Assessment**"),
    subtitle = md("Summary Descriptives CFA Sample (n=262)")
  ) %>% 
  # tab_footnote(
  #   footnote = md("**Histogram**"),
  #   locations = cells_column_labels(columns = hist_data)
  # ) %>%
  # tab_footnote(
  #   footnote = md("**Density**"),
  #   locations = cells_column_labels(columns = dens_data)
  # ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = (""),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5: Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F4: Using light before bedtime**"),
      rows = c(15,16,17,19) 
        ) %>% 
  tab_row_group(
      label = md("**F3: Using phone and smart-watch in bed**"),
      rows = c(2,13,14,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F2: Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1: Wearing blue light filters**"),
      rows = c(10,11,18) 
        ) %>% 
  gtsave("Supplimentary_materials/S_Figure/S2_Fig.png",vwidth = 7000)

@@

png(filename="Figures/CFAplot2.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

knitr::include_graphics("Figures/CFAplot.png", dpi =600)

@@

ggsave("Figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")

@@

ggsave("Figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")

@@

TIC.plot <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 3,
                     label_size = 15,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")

@@

knitr::include_graphics('Figures/TIC.png', dpi =600)
```
